Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-04-20 paper/current/main.tex
removed extra incomplete reference

Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space.
Accordingly, prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis.
Universities at the bottom of this axis tend to be regional universities with lower national profiles.
By considering mobility between all organization types, organization embeddings offer a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c)
\ref{fig:supp:sem

>>>>

Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space.
Accordingly, prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis.
Universities at the bottom of this axis tend to be regional universities with lower national profiles.
By considering mobility between all organization types, organization embeddings offer a new means of reasoning about the prestige of organizations typically excluded from rankings such as government organizatioss (Fig.~\ref{fig:supp:semaxis_sectors}a), research institutes (Fig.~\ref{fig:supp:semaxis_sectors}b), and teaching colleges (Fig.~\ref{fig:supp:semaxis_sectors}c).
